\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration2.tex
changed grammar

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{This figure shows an empirical measurement of IR intensity at different positions. We measure the intensity at a plane every meter away from the IR emitter. On that plane, a sample is mesaured every 5 centimeters, \changes{and we stop when the reading is smaller than ambient noise.} \changes{To match with our assumption about the relationship between angles and intensities, the vertical axis is changed to the degree of the angle.} The size and color brightness in this graph represents the intensity readings for visualization.}
\label{fig:measurement}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{This figure shows an empirical measurement of IR intensity at different positions. We measure the intensity at a plane every meter away from the IR emitter. On that plane, a sample is taken every 5 centimeters, \changes{and we stop when the reading is smaller than ambient noise.} \changes{To match our assumption about the relationship between angles and intensities, the vertical axis is changed to the degree of the angle.} The size and color brightness represent the intensity of the readings for visualization.}
\label{fig:measurement}
\end{figure}
